---
title: "Directed Graph Model"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

## Load data
```{r message=FALSE, warning=FALSE}
load("newspapers.RData")
#load("newspapers_un.Rdata")    
#load("ntotal.RData")
library(ggraph)
library(tidygraph)
library(dplyr)
library(igraph)
library(sna)
```

## Graph Construction
Construction of vertices and weighted edges list for the directed weighted model:
```{r message=FALSE, warning=FALSE}
vertices <- data.frame(id=unique(c(newspapers$n1)))

newspapers %>%  transform(weight1 = nshare/f1) %>%
  select(from=n1, to=n2,weight1) %>% 
  distinct(from,to,weight1) -> edges
```

## Pregraph analysis 
Analyze edge weights distribution (plot of weights for the directed model):
```{r}
# mean and deviation of weight1
mean1 <- mean(edges$weight1)
median1 <- median(edges$weight1)
sd1 <- sd(edges$weight1,na.rm = F)

cat('Mean of weigh1: ' ,mean1,'\n', 'Standard deviation of weight1: ', sd1, '\n\n', sep='')

coefprob <- 0.2

hist(edges$weight1, breaks=100) 
abline(v = mean1, col = "black", lwd = 2)
abline(v = -mean1*log(coefprob), col = "blue", lwd = 2)
abline(v = quantile(edges$weight1)[4], col = "red", lwd = 2)
legend(x="right",legend=c("mean", "3rd quartile", "Threshold with null model"),
       col=c("black", "red", "blue"),lty=1, lwd=1, cex=0.8)
#(v = median1, col = "red", lwd = 2)

```

We observe an exponential-like distribution for the weights in the network. We propose thresholds using an exponential null model using the mean for the observed network to construct the parameter. This represents a conservative method to detect edges with weights above expected and allows to have some probabilistic interpretation for filtering. We filter the edges with high weight, unlikely to happen under the exponential distribution i.e. with probability lower than p. Threshold is thus -mean1*log(p).


Computation of indegrees and outdegrees for the weighted unfiltered network:
```{r}
edges %>% select(-"from") %>% group_by(to) %>% summarise(indeg= sum(weight1)) %>% rename("id" = "to")  -> indegs

edges %>% select(-"to") %>% group_by(from) %>% summarise(indeg= sum(weight1)) %>% rename("id" = "from") -> outdegs

degs <- merge(outdegs, indegs, by ="id")
```

## Analyze graph filtered by thresholds 
Compute of betweeness centrality for different thresholds: (not used in report)

```{r fig.height=10, fig.width=13}
d_graph <- tbl_graph(nodes=vertices, edges = edges, node_key = "id", directed = TRUE)
d_graph %>% 
  ggraph(layout="fr") + geom_edge_fan(color="lightblue",
                        strength = 1,
                        arrow = arrow(length = unit(1, 'mm'), type = 'closed'),
                        end_cap = circle(2, 'mm'),
                        show.legend = T) +
  geom_node_point(color="red") + 
  geom_node_text(aes(label = id),nudge_y = 0, repel = FALSE)+theme_graph()+
  ggtitle(paste('Directed Weighted Graph-No filter', sep = ''))
```

```{r echo=TRUE, fig.height=10, fig.width=13}
btwss <- data.frame("id" =vertices)
probs <- c(0.2,0.1,0.05)

for (i in 1:length(probs)){
p <- probs[i]
d_graph %>% activate(edges) %>%  filter( weight1 > -mean1*log(p) ) %>% activate(nodes) %>% mutate(deg = centrality_degree(mode="in"))-> d_graphcc1
  
bts <- igraph::betweenness(d_graphcc1)
btwss[paste("Betweeness for threshold", toString(-mean1*log(p)), sep = ' ')] <- bts


print(d_graphcc1 %>% 
  ggraph(layout="fr") +  geom_edge_fan(color="lightblue",
                        strength = 2,
                        arrow = arrow(length = unit(2, 'mm'), type = 'closed'),
                        end_cap = circle(2, 'mm'),
                        show.legend = T)+ 
  geom_node_point(color="red", aes(size = deg)) + 
  geom_node_text(aes(label = id),nudge_y = 0, repel = FALSE)+
  theme_graph()+labs(deg = 'Out Degree')+
  ggtitle(paste('Directed Weighted Graph with threshold ', -mean1*log(p), sep = '')))



#ggsave(paste('plot/df_p_',p, '.png', sep = ''), width = 10, height = 10, units = 'in')
}

degs <- merge(degs, btwss, by ="id")

#library("writexl")
#write_xlsx(degs,"degs.xlsx")
```




## CUG Test
CUG tests for basic network structures (here transitivity) for the unweighted directed graph for some threshold: (not used)

```{r}

p <-0.2
d_graph %>% activate(edges) %>%  filter( weight1 > -mean1*log(p) ) %>% activate(nodes) %>% mutate(deg = centrality_degree(mode="in"))-> d_graphcc1


AdjMat <- as.matrix(as_adjacency_matrix(d_graphcc1, attr = "weight1"))
AdjMat[which(AdjMat != 0)] <- 1

sna::cug.test(AdjMat, gtrans, cmode="size")

```