---
title: "Undirected Experimental Graph Analysis"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

# Load data

"newspapers_un.Rdata" is for undirected graph. Since there is no direction for edges, it only has half of the rows comparing with "newspapers.Rdata".

"ntotal.Rdata" is the total number of twitter followers in the newspaper space of interests.

Our domain includes 27 newspapers (after preprocess).


```{r load data, warning=FALSE}
# Create plot directory, if it doesn't exist
dir.create("plot", showWarnings = F)

#load("newspapers.Rdata")    
load("newspapers_un.Rdata")    
load("ntotal.RData")
library(ggraph)
library(tidygraph)
library(dplyr)
library(igraph)

```

# Construct undirected graph

## Create vertices and edges
```{r undirected vertices and edges, warning=FALSE}
vertices <- data.frame(id=unique(c(newspapers_un$n1,newspapers_un$n2)))

# Add newspaper attributes
load("newsAttributes.RData")
verticesMerged <- inner_join(vertices, newsAttributes)

newspapers_un %>%  transform(weight = nshare/nunion) %>%
  select(from=n1, to=n2,weight) %>% 
  distinct(from,to,weight) -> edges

# mean and deviation of weight2
mean2 <- mean(edges$weight)
sd2 <- sd(edges$weight,na.rm = F)
cat('Mean of weigh2: ' ,mean2,'\n', 'Standard deviation of weight2: ', sd2, '\n\n', sep='')
```


## Draw unfiltered graph
```{r undirected no filtered graph, fig.height=10, fig.width=13, warning=FALSE}
dir.create("plot/Model1Undirected", showWarnings = F)

ud_graph <- tbl_graph(nodes=verticesMerged, edges = edges, node_key = "id", directed = F)
ud_graph %>% 
  ggraph(layout="fr") + geom_edge_fan(color="lightblue",
                        alpha = .7,
                        show.legend = T) +
  geom_node_point(color="red") +
  geom_node_text(aes(label = id),nudge_y = 0, repel = F) + theme_graph() +
  ggtitle(paste('Undirected Weighted Graph-No filter', sep = ''))


#ggsave(paste('plot/Model1Undirected/ud', '.png', sep = ''), width = 10, height = 10, #units = 'in')

```

## Community Analysis

```{r filtered undirected graph by threshold with communities}
for (i in c(-2,-1,-0.5,-0.4,-0.35,-0.3,-0.25,-0.2,-0.15,-0.1,-0.05,0,1,2)){ 
  ud_graph %>% activate(edges) %>% mutate(new_weight = (weight-mean2)/sd2)  %>% filter( new_weight > i ) %>% activate(nodes) %>% mutate(deg = centrality_degree()) %>% activate(nodes) %>% mutate(community = as.character(group_louvain())) -> ud_graphcc1
  
  ud_graphcc1 %>% 
    ggraph(layout="fr") +  geom_edge_fan(color="lightblue",
                        strength = 2,
                        end_cap = circle(2, 'mm'),
                        show.legend = T)+ 
    geom_node_point(aes(color = community, size = deg)) + 
    geom_node_text(aes(label = id),nudge_y = 0, repel = FALSE)+
    theme_graph()+labs(deg = 'Total Degree')+
    ggtitle(paste('Undirected Weighted Graph with threshold ', i, sep = ''))

#  ggsave(paste('plot/Model1Undirected/udf_t_',i, '.png', sep = ''), width = 10, #height = 10, units = 'in')
}
```


## Modularity and Assortativity Analysis
```{r get modularity and assortativity} 
threshold <- -0.3
print(paste("Threshold: ", threshold))

ud_graph %>% activate(edges) %>% mutate(new_weight = (weight-mean2)/sd2)  %>% filter( new_weight > threshold ) %>% activate(nodes) %>% mutate(deg = centrality_degree()) %>% activate(nodes) %>% mutate(community = as.character(group_louvain())) -> ud_graphcc2

print("Modularity:")
ud_graphcc2 %>% 
  mutate(modularity = graph_modularity(community)) %>% 
  pull(modularity) %>% 
  head(1)

print("Assortativity:")
ud_graphcc2 %>% 
  mutate(assort = graph_assortativity(community)) %>% 
  pull(assort)  %>% 
  head(1)
```

# Graph With Attributes


```{r graph with attributes1, fig.height=10, fig.width=15, warning=FALSE}
threshold <- -0.3
print(paste("Threshold: ", threshold))

ud_graph <- tbl_graph(nodes=verticesMerged, edges = edges, node_key = "id", directed = F)

ud_graph %>% activate(edges) %>% mutate(new_weight = (weight-mean2)/sd2)  %>% filter( new_weight > threshold ) %>%  activate(nodes) %>% mutate(deg = centrality_degree()) %>%
    ggraph(layout="fr") + geom_edge_fan(color="lightblue",
                        strength = 2,
                        show.legend = T) +
    geom_node_point(aes(
            colour = as.factor(PoliticalOrientation),
      shape = as.factor(Seriousness),
      size = deg
    ),
    show.legend = T) + 
     labs(colour = 'PoliticalOrientation', shape = 'Seriousness', size = 'Degree')+
    geom_node_text(aes(label = id), nudge_y = 0, repel = F)+
    theme_graph()+ggtitle(paste('Undirected Weighted Graph With Attributes - ','gamma ',threshold, sep = ''))


ggsave(paste('plot/Model1Undirected/ud_attr_g',threshold, '.png', sep = ''), width = 15, height = 10, units = 'in')

```

```{r graph with attributes2, fig.height=10, fig.width=15, warning=FALSE}
threshold <- -0.3
print(paste("Threshold: ", threshold))

ud_graph <- tbl_graph(nodes=verticesMerged, edges = edges, node_key = "id", directed = F)

ud_graph %>% activate(edges) %>% mutate(new_weight = (weight-mean2)/sd2)  %>% filter( new_weight > threshold ) %>%  activate(nodes) %>% mutate(deg = centrality_degree()) %>%
    ggraph(layout="fr") + geom_edge_fan(color="lightblue",
                        strength = 2,
                        show.legend = T) +
    geom_node_point(aes(
      colour = as.factor(Topic),
      shape = as.factor(Location),
      size = deg
    ),
    show.legend = T) + 
     labs(colour = 'Topic', shape = 'Location', size = 'Degree')+
    geom_node_text(aes(label = id), nudge_y = 0, repel = F)+
    theme_graph()+ggtitle(paste('Undirected Weighted Graph With Attributes - ','gamma ',threshold, sep = ''))


#ggsave(paste('plot/Model1Undirected/ud_attr1_g',threshold, '.png', sep = ''), width = #15, height = 10, units = 'in')

```

