

---
title: "Data Preprocessing"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

## Clean Data
To analyze newspapers with multiple accounts, we firstly transfer all data of unique accounts.

```{r warning=FALSE}
dir.create("CleanData", showWarnings = F)

# Financial Times

load("Follower lists/FinancialTimes.RData")
load("Follower lists/FT.RData")
commonFols <- merge(FinancialTimes, FT)
print(nrow(commonFols))
# 2224889
# Overlap of approx. 50%, while the FinancialTimes account focuses only focuses on
# breaking news and insights, the FT account also adds "big stories", hence we
# will merge their followers together
FTmerged <- merge(FinancialTimes, FT, all = T) # 9127337
save(FTmerged, file="CleanData/FinancialTimes.RData")

# Guardian

load("Follower lists/guardian.RData")
load("Follower lists/guardiannews.RData")
commonFols <- merge(guardian, guardiannews)
print(nrow(commonFols))
# 2339838
# Overlap is very high, guardian covers gaurdiannews content (+ additional topics),
# therefore, will be merged into single node in graph
Gmerged <- merge(guardian, guardiannews, all = T) # 10731460
save(Gmerged, file="CleanData/guardian.RData")

# Daily Mail

load("Follower lists/MailOnline.RData")
load("Follower lists/DailyMailUK.RData")
commonFols <- merge(DailyMailUK, MailOnline)
print(nrow(commonFols))
# 293912
# Overlap is quite high, coverage broadly includes the same content
# therefore, will be merged into single node in graph
Mailmerged <- merge(DailyMailUK, MailOnline, all = T) # 2836576
save(Mailmerged, file="CleanData/MailOnline.RData")

# The Sun

load("Follower lists/TheSun.RData")
load("Follower lists/Fabulousmag.RData")
commonFols <- merge(TheSun, Fabulousmag)
print(nrow(commonFols))
# 18695
# Overlap is low and second account has too few followers to be relevant, so it will be droped
# Also allows us to consider The Sun and The Sun on Sundays as a single newspaper
save(TheSun, file="CleanData/TheSun.RData")

# Evening Standard

load("Follower lists/EveningStandard.RData")   # 131560
load("Follower lists/standardnews.RData")      # 639703 - most followed!
load("Follower lists/standardsport.RData")     #  42006
load("Follower lists/standardcity.RData")      #   7791
commonFols <- merge(standardnews, EveningStandard)
print(nrow(commonFols))
# 90125
# Very high overlap, a clear mojority of the EveningStandard account followers 
# are here for the news, hence the two accounts will be merged

commonFols <- merge(standardnews, standardsport)
print(nrow(commonFols))
# 6245
commonFols <- merge(standardsport, EveningStandard)
print(nrow(commonFols))
# 3599
# Low overlap with news account (and general one), we can deduce that standardsport
# is followed by different people (but the sample is still too small for relevance)

commonFols <- merge(standardnews, standardcity)
print(nrow(commonFols))
# 3715
commonFols <- merge(standardcity, EveningStandard)
print(nrow(commonFols))
# 2195
commonFols <- merge(standardcity, standardsport)
print(nrow(commonFols))
# 372
# The city account focuses on London. The is significant overlap with the 
# standardnews account, but much less with the general account, so it will be discarded

# Merge two main accounts
ESmerged <- merge(standardnews, EveningStandard, all = T) # 681138
save(ESmerged, file="CleanData/standardnews.RData")

# Metro

load("Follower lists/MetroUK.RData")
load("Follower lists/MetroScotland.RData")
commonFols <- merge(MetroUK, MetroScotland)
print(nrow(commonFols))
# 406
# Overlap is low, but Scotland account has too few followers to be relevant
save(MetroUK, file="CleanData/MetroUK.RData")

# Daily Star

load("Follower lists/dailystar.RData")
load("Follower lists/DStarPics.RData")
commonFols <- merge(dailystar, DStarPics)
print(nrow(commonFols))
# 4096
# The DStarPics account has too few followers to be relevat to our network
save(dailystar, file="CleanData/dailystar.RData")
```

## Construct Dataframe
Further, we construct dataframes for graph construction later. Both directed and undirected cases are considered.

To run this part, please make sure that directory: "CleanData" is available. Or you can directly start from chunk: "load data".

Construct dataframe for directed graph.
```{r directed data, warning=FALSE}
route = "CleanData"
files <- list.files(route, pattern="*.RData")

newspapers <- data.frame(matrix(ncol = 6, nrow = 0))
names <- c("n1", "n2", "f1","f2","nshare","nunion")
colnames(newspapers) <- names

temp=1
for (i in c(1:length(files))){
  name1 <- load(paste(route, "/",files[i], sep = ""))
  target1 <- get(ls()[ls() == name1])
  f1 <- length(target1$user_id)
  
  for (j in c(1:length(files))){
    if(i != j){
  cat(i,", ",j,sep="")
  name2 <- load(paste(route, "/",files[j], sep = ""))
#  cat(name1,", ",name2,sep="")
  target2 <- get(ls()[ls() == name2])
  f2 <- length(target2$user_id)
  nshare <- length(intersect(target1$user_id,target2$user_id))
  nunion <- length(union(target1$user_id,target2$user_id))
  newspapers[temp,] = c(name1,name2,f1,f2,nshare,nunion)
  temp <- temp + 1
    }
  }
}

newspapers <- transform(newspapers, f1=as.numeric(f1),f2=as.numeric(f2),nshare=as.numeric(nshare),nunion=as.numeric(nunion))

#save(newspapers, file="newspapers.RData")
```

Construct dataframe for undirected graph.
```{r undirected data, warning=FALSE}
route = "CleanData"
files <- list.files(route, pattern="*.RData")

newspapers_un <- data.frame(matrix(ncol = 6, nrow = 0))
names <- c("n1", "n2", "f1","f2","nshare","nunion")
colnames(newspapers_un) <- names
temp=1
for (i in c(1:length(files))){
  name1 <- load(paste(route, "/",files[i], sep = ""))
  target1 <- get(ls()[ls() == name1])
  f1 <- length(target1$user_id)
  
  for (j in c(i:length(files))){
    if(i != j){
  cat(i," ",j,",",sep="")
  name2 <- load(paste(route, "/",files[j], sep = ""))
#  cat(name1,", ",name2,sep="")
  target2 <- get(ls()[ls() == name2])
  f2 <- length(target2$user_id)
  nshare <- length(intersect(target1$user_id,target2$user_id))
  nunion <- length(union(target1$user_id,target2$user_id))
  newspapers_un[temp,] = c(name1,name2,f1,f2,nshare,nunion)
  temp <- temp + 1
    }
  }
}

newspapers_un <- transform(newspapers_un, f1=as.numeric(f1),f2=as.numeric(f2),nshare=as.numeric(nshare),nunion=as.numeric(nunion))

#save(newspapers_un, file="newspapers_un.RData")
```

Compute total users in domain.
```{r total ids, warning=FALSE}
route = "CleanData"
files <- list.files(route, pattern="*.RData")
ids <- c()

for (i in c(1:length(files))){

  cat(i,sep="")
  name <- load(paste(route, "/",files[i], sep = ""))
  target <- get(ls()[ls() == name])
  ids <- union(ids,target$user_id)
}

ntotal <- length(ids)
cat('Total numebr of ids: ',ntotal, sep = "")
#save(ntotal, file="ntotal.RData")
```
