---
title: "Undirected Probabilistic Graph Analysis"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

# Load Data

"newspapers_un.Rdata" is for undirected graph. Since there is no direction for edges, it only has half of the rows comparing with "newspapers.Rdata".

"ntotal.Rdata" is the total number of twitter followers in the newspaper space of interests.

Our domain includes 27 newspapers (after preprocess).


```{r load data, message=FALSE, warning=FALSE}
#load("newspapers.RData")
load("newspapers_un.RData")
load("ntotal.RData")
load("newsAttributes.RData")
library(ggraph)
library(tidygraph)
library(dplyr)
library(igraph)
library(assortnet)

newsAttributes$Topic <- ifelse(newsAttributes$Topic=="General", "General", "Specific")
newsAttributes$Broadness <- ifelse(newsAttributes$Location == "Local" | newsAttributes$Topic == "Specific"   , "Specific","Broad")
newsAttributes$Location <- factor(newsAttributes$Location)
newsAttributes$Broadness <- factor(newsAttributes$Broadness)
newsAttributes$Topic <- factor(newsAttributes$Topic)
newsAttributes$Format <- factor(newsAttributes$Format)
newsAttributes$Seriousness <- factor(newsAttributes$Seriousness)
newsAttributes$PoliticalOrientation <- factor(newsAttributes$PoliticalOrientation)
```



# Construct Graph
## Undirected filtered graph
Use Binomial distributed edges.
```{r graph with binomial edges assumption, fig.height=10, fig.width=15, warning=FALSE}
vertices <- data.frame(id=unique(c(newspapers_un$n1,newspapers_un$n2)))
vertices<-merge(x = vertices, y = newsAttributes)

for (gamma in c(3)){

newspapers_un %>% 
    transform(w1= f1/ntotal,w2= f2/ntotal) %>% 
    transform(avg_weight = ntotal*w1*w2,sd_weight = sqrt(ntotal*w1*w2*(1-w1*w2))) %>%
    select(from=n1, to=n2,nshare,avg_weight,sd_weight) %>%
    filter((nshare-avg_weight)/sd_weight > gamma ) %>%
    distinct() -> edges
  
ud_graph <- tbl_graph(nodes=vertices, edges = edges, node_key = "id", directed = FALSE)
ud_graph %>% 
  activate(nodes) %>% activate(edges) %>% mutate(Shared_followers=nshare)->ud_graph 


ud_graph %>% ggraph() + geom_node_point(colour="red", size=3) + geom_edge_link(aes(color=Shared_followers,width=Shared_followers))  + geom_node_text(size=6,color='white',aes(label=id)) +  theme_graph(background ='grey')
#(paste('plot/udf_bi_g',gamma, '.png', sep = ''), width = 10, height = 10, units = 'in')

}
```
## Graph Analysis
### Compute assortativities
```{r Assortativity, warning=FALSE}
ud_graph %>% 
  activate(nodes) %>% activate(edges) %>% mutate(weight=nshare)->ud_graph 

ud_graph %>% 
  activate(nodes) %>% 
  mutate(deg=centrality_degree()) %>% 
  mutate(assort = graph_assortativity(attr=deg))%>% 
  mutate(assort_polit = graph_assortativity(attr=PoliticalOrientation))%>% 
  mutate(assort_seriousness = graph_assortativity(attr=Seriousness))%>% 
  mutate(assort_format = graph_assortativity(attr=Format))%>% 
  mutate(assort_topic = graph_assortativity(attr=Topic))%>% 
  mutate(assort_Location = graph_assortativity(attr=Location))%>% 
  mutate(assort_Broadness = graph_assortativity(attr=Broadness))->ud_graph 

ud_graph%>% pull(assort) %>% head(1)
ud_graph%>% pull(assort_polit) %>% head(1)
ud_graph%>% pull(assort_seriousness) %>% head(1)
ud_graph%>% pull(assort_format) %>% head(1)
ud_graph%>% pull(assort_topic) %>% head(1)
ud_graph%>% pull(assort_Location) %>% head(1)
ud_graph%>% pull(assort_Broadness) %>% head(1)
```

### Find communities
```{r Find communities}
ud_graph %>% 
  activate(nodes) %>% 
  mutate(community=as.character(group_louvain(weights = NULL))) -> ud_graph

ud_graph %>% 
  activate(nodes) %>% 
  as_tibble()
```

Compute assortativities based on communities
```{r}

ud_graph %>% 
  activate(nodes) %>% 
  mutate(assort_comm = graph_assortativity(attr=community))->ud_graph 

ud_graph%>% pull(assort_comm) %>% head(1)

```

### Modularity without weights
```{r Compute modularity without weights}
ud_graph %>% 
  activate(nodes) %>% mutate(modularity = graph_modularity(group=deg)) %>% 
  mutate(modularity_comm = graph_modularity(group=community)) %>% 
  mutate(modularity_polit = graph_modularity(group=PoliticalOrientation)) %>% 
  mutate(modularity_seriousness = graph_modularity(group=Seriousness)) %>% 
  mutate(modularity_format = graph_modularity(group=Format)) %>% 
  mutate(modularity_topic = graph_modularity(group=Topic)) %>% 
  mutate(modularity_Location = graph_modularity(group=Location))%>% 
  mutate(modularity_Broadness = graph_modularity(group=Broadness))->ud_graph
  
ud_graph %>% pull(modularity) %>% head(1)
ud_graph %>% pull(modularity_comm) %>% head(1)
ud_graph %>% pull(modularity_polit) %>% head(1)
ud_graph %>% pull(modularity_seriousness) %>% head(1)
ud_graph %>% pull(modularity_format) %>% head(1)
ud_graph %>% pull(modularity_topic) %>% head(1)
ud_graph %>% pull(modularity_Location) %>% head(1)
ud_graph %>% pull(modularity_Broadness) %>% head(1)
```

### Centralities and K core
```{r Centralities and k core, warning=FALSE}
ud_graph %>% activate(nodes) %>%
 mutate(deg_cen = centrality_degree()) %>%
 mutate(close_cen = centrality_closeness()) ->ud_graph
ud_graph %>%  activate(nodes) %>%  mutate(kcore=as.factor(node_coreness())) ->ud_graph
ud_graph%>% arrange(desc(deg_cen)) %>% as_tibble() %>% head(10)
ud_graph %>% as_tibble() -> proba_model_results
#save(data=proba_model_results,file = "./proba_model_results.RData")
```

### Graph plot
```{r Graphs, fig.height=10, fig.width=15, warning=FALSE}

ud_graph %>% ggraph()  + geom_edge_link(aes(color=Shared_followers,width=Shared_followers))  + geom_node_text(size=6,color='black',aes(label=id)) +  theme_graph(background ='white') + geom_node_point(size=3,aes(color=community))+ scale_edge_colour_gradient2(low = "white",mid = "grey",high = "black",midpoint = 0,space = "Lab",na.value = "grey50",guide = "edge_colourbar") + ggtitle(paste('Binomial Model Graph Communities  ', sep = ''))

ud_graph %>% ggraph()  + geom_edge_fan(color="lightblue", strength = 2, show.legend = T)   + geom_node_text(size=6,color='black',aes(label=id)) +  theme_graph(background ='white') + geom_node_point(size=3,aes(color=community))+ scale_edge_colour_gradient2(low = "white",mid = "grey",high = "black",midpoint = 0,space = "Lab",na.value = "grey50",guide = "edge_colourbar") + ggtitle(paste('Binomial Model Graph Communities  ', sep = ''))

ud_graph %>% ggraph()  + geom_edge_link(aes(color=Shared_followers,width=Shared_followers))  + geom_node_text(size=6,color='black',aes(label=id)) +  theme_graph(background ='white') + geom_node_point(size=3,aes(color=kcore))+ scale_edge_colour_gradient2(low = "white",mid = "grey",high = "black",midpoint = 0,space = "Lab",na.value = "grey50",guide = "edge_colourbar") + ggtitle(paste('Binomial Model Graph K cores', sep = ''))


ud_graph %>% ggraph()  + geom_edge_fan(color="lightblue", strength = 2, show.legend = T)  + geom_node_text(size=6,color='black',aes(label=id)) +  theme_graph(background ='white') + geom_node_point(size=3,aes(color=kcore))+ scale_edge_colour_gradient2(low = "white",mid = "grey",high = "black",midpoint = 0,space = "Lab",na.value = "grey50",guide = "edge_colourbar") + ggtitle(paste('Binomial Model Graph K cores', sep = ''))

ud_graph %>% ggraph()  + geom_edge_link(aes(color=Shared_followers,width=Shared_followers))  + geom_node_text(size=6,color='black',aes(label=id)) +  theme_graph(background ='white') + geom_node_point(size=3,aes(color=Broadness))+ scale_edge_colour_gradient2(low = "white",mid = "grey",high = "black",midpoint = 0,space = "Lab",na.value = "grey50",guide = "edge_colourbar") + ggtitle(paste('Binomial Model Graph by Broadness  ', sep = ''))

ud_graph %>% ggraph()  + geom_edge_fan(color="lightblue", strength = 2, show.legend = T)  + geom_node_text(size=6,color='black',aes(label=id)) +  theme_graph(background ='white') + geom_node_point(size=3,aes(color=Broadness))+ scale_edge_colour_gradient2(low = "white",mid = "grey",high = "black",midpoint = 0,space = "Lab",na.value = "grey50",guide = "edge_colourbar") + ggtitle(paste('Binomial Model Graph by Broadness  ', sep = ''))

```

```{r fig.height=10, fig.width=15, warning=FALSE}
ud_graph %>% ggraph()  + geom_edge_fan(color="lightblue", strength = 2, show.legend = T)  + geom_node_text(size=6,color='black',aes(label=id)) +  theme_graph(background ='white') + geom_node_point(size=4,aes(color=kcore))+ scale_edge_colour_gradient2(low = "white",mid = "grey",high = "black",midpoint = 0,space = "Lab",na.value = "grey50",guide = "edge_colourbar") + ggtitle(paste('Binomial Model Graph K cores', sep = ''))
#ggsave(paste('plot/binomial_kcores', '.png', sep = ''), width = 15, height = 10, units = 'in')


ud_graph %>% ggraph()  + geom_edge_fan(color="lightblue", strength = 2, show.legend = T)   + geom_node_text(size=6,color='black',aes(label=id)) +  theme_graph(background ='white') + geom_node_point(size=4,aes(color=community))+ scale_edge_colour_gradient2(low = "white",mid = "grey",high = "black",midpoint = 0,space = "Lab",na.value = "grey50",guide = "edge_colourbar") + ggtitle(paste('Binomial Model Graph Communities  ', sep = ''))
#ggsave(paste('plot/binomial_communities', '.png', sep = ''), width = 10, height = 10, units = 'in')

ud_graph %>% ggraph()  + geom_edge_fan(color="lightblue", strength = 2, show.legend = T)  + geom_node_text(size=6,color='black',aes(label=id)) +  theme_graph(background ='white') + geom_node_point(size=4,aes(color=Broadness))+ scale_edge_colour_gradient2(low = "white",mid = "grey",high = "black",midpoint = 0,space = "Lab",na.value = "grey50",guide = "edge_colourbar") + ggtitle(paste('Binomial Model Graph by Broadness  ', sep = ''))
#ggsave(paste('plot/binomial_Broadness', '.png', sep = ''), width = 15, height = 10, units = 'in')
```

```{r graph with attributes, fig.height=10, fig.width=15, warning=FALSE}
vertices <- data.frame(id=unique(c(newspapers_un$n1,newspapers_un$n2)))
verticesMerged <- inner_join(vertices, newsAttributes)

gamma <- 0

  newspapers_un %>% 
    transform(w1= f1/ntotal,w2= f2/ntotal) %>% 
    transform(avg_weight = ntotal*w1*w2,sd_weight = sqrt(ntotal*w1*w2*(1-w1*w2))) %>%
    select(from=n1, to=n2,nshare,avg_weight,sd_weight) %>%
    filter((nshare-avg_weight)/sd_weight > gamma ) %>%
    distinct() -> edges

  ud_graph <- tbl_graph(nodes=verticesMerged, edges = edges, node_key = "id", directed = F)
  ud_graph %>%  activate(nodes) %>% mutate(deg = centrality_degree()) %>%
    ggraph(layout="fr") + geom_edge_fan(color="lightblue",
                        strength = 2,
                        show.legend = T) +
    geom_node_point(aes(
      colour = as.factor(PoliticalOrientation),
      shape = as.factor(Seriousness),
      size = deg
    ),
    show.legend = T) + 
     labs(colour = 'PoliticalOrientation', shape = 'Seriousness', size = 'Degree')+
    geom_node_text(aes(label = id), nudge_y = 0, repel = F)+
    theme_graph()+
    ggtitle(paste('Undirected Weighted Graph With Attributes(binomial filter) - gamma ', gamma, sep = ''))

#  ggsave(paste('plot/udf_bi_attr_g',gamma, '.png', sep = ''), width = 13, height = 10, units = 'in')
```

```{r graph with other attributes, fig.height=10, fig.width=15, warning=FALSE}

gamma <- 0

  newspapers_un %>% 
    transform(w1= f1/ntotal,w2= f2/ntotal) %>% 
    transform(avg_weight = ntotal*w1*w2,sd_weight = sqrt(ntotal*w1*w2*(1-w1*w2))) %>%
    select(from=n1, to=n2,nshare,avg_weight,sd_weight) %>%
    filter((nshare-avg_weight)/sd_weight > gamma ) %>%
    distinct() -> edges

  ud_graph <- tbl_graph(nodes=verticesMerged, edges = edges, node_key = "id", directed = F)
  ud_graph %>%  activate(nodes) %>% mutate(deg = centrality_degree()) %>%
    ggraph(layout="fr") + geom_edge_fan(color="lightblue",
                        strength = 2,
                        show.legend = T) +
    geom_node_point(aes(
      colour = as.factor(Topic),
      shape = as.factor(Location),
      size = deg
    ),
    show.legend = T) + 
     labs(colour = 'Topic', shape = 'Location', size = 'Degree')+
    geom_node_text(aes(label = id), nudge_y = 0, repel = F)+
    theme_graph()+
    ggtitle(paste('Undirected Weighted Graph With Attributes(binomial filter) - gamma ', gamma, sep = ''))

#  ggsave(paste('plot/udf_bi_attr1_g',gamma, '.png', sep = ''), width = 13, height = 10, units = 'in')
```
